\problemname{Farey Sums}

\noindent
Given a positive integer, $N$, the sequence of all fractions $a / b$ with
$(0 < a \le b), (1 \le b \le N)$ and $a$ and $b$ relatively prime,
listed in increasing order, is called the \emph{Farey Sequence of order N}.

\noindent
For example, the \emph{Farey Sequence of order 6} is:

\begin{center}
    $\frac{0}{1}, 
     \frac{1}{6},
     \frac{1}{5},
     \frac{1}{4},
     \frac{1}{3},
     \frac{2}{5},
     \frac{1}{2},
     \frac{3}{5},
     \frac{2}{3},
     \frac{3}{4},
     \frac{4}{5},
     \frac{5}{6},
     \frac{1}{1}
    $
\end{center}

If the denominators of the \emph{Farey Sequence of order N} are:

\begin{center}
$b_1, b_2, \ldots, b_K$
\end{center}

then the \emph{Farey Sum of order N} is the sum of $b_i / b_{i+1}$ from $i = 1 \ldots K-1$.

For example, the \emph{Farey Sum of order 6} is:

\begin{center}
$\frac{1}{6}
+\frac{6}{5}
+\frac{5}{4}
+\frac{4}{3}
+\frac{3}{5}
+\frac{5}{2}
+\frac{2}{5}
+\frac{5}{3}
+\frac{3}{4}
+\frac{4}{5}
+\frac{5}{6}
+\frac{6}{1}
=
\frac{35}{2}
$
\end{center}

Write a program to compute the \emph{Farey Sum of order N} (input)!

\section*{Input}

The first line of input contains a single integer $P$, ($1 \le P \le 9999$),
which is the number of data sets that follow.  Each data set should be
processed identically and independently.

Each data set consists of a single line of input.  It contains the data
set number, $K$, followed by the order $N$, ($2 \le N \le 10000$), of the
\emph{Farey Sum} that is to be computed.

\section*{Output}

For each data set there is a single line of output.  The single output
line consists of the data set number, $K$, followed by a single space
followed by the \emph{Farey Sum} as a decimal fraction in lowest terms.  If the
denominator is $1$, print only the numerator.

